Learning and comparing functional connectomes across subjects

### 2013-01-01 paper.tex
iter

The interpretation of the predictive model can be complicated and
requires insight into the mechanisms
underlying the modeling approach. For linear classifiers, 
classifier weights are similar to the weights of a ordinary regression.
If features are appropriately
standardized prior to training, the magnitude of weights can be
interpreted to reflect the relative importance of the feature to the
model, but interpreting how the feature differs between classes or
relates to a continuous variable is more complicated, particularly given
the multivariate nature of their involvement\footnote{Note that there is
typically no statistical framework for thresholding these weights, and
meaningless features are not always set to zero (this is particularly the
case for $\ell_2$ regularized algorithms such as SVM and ridge
regression)}. For classification methods
such as Fisher's linear discriminant analysis (LDA), which maximally
separates class means given their standard deviation, feature weights are
representative of the differences between class means. For support vector
classification, classifier weights are derived from observations that are
the most similar between classes, and hence represents the border between
classes. To draw conclusions on the features used for prediction, it is
perhaps most reasonable to adapt a conservative interpretation in which
predictive models is used to identify the most relevant features that are
later tested in follow-up experiments better suited to elucidating their
relationship to the variable of interest.

>>>>

The interpretation of the predictive model can be complicated and
requires insight into the mechanisms
underlying the modeling approach. For linear classifiers, 
classifier weights are similar to the weights of a ordinary linear regression.
If features are appropriately
standardized prior to training, the magnitude of weights can be
interpreted to reflect the relative importance of the feature to the
model. However, interpreting how the feature differs between classes or
relates to a continuous variable can be more complicated given
the multivariate nature of their involvement\footnote{Note that there is
typically no statistical framework for thresholding these weights, and
meaningless features are not always set to zero (this is particularly the
case for $\ell_2$ regularized algorithms such as SVM and ridge
regression)}. For classification methods
such as Fisher's linear discriminant analysis (LDA), which maximally
separates class means given their standard deviation, feature weights are
representative of the differences between class means. For support vector
classification, classifier weights are derived from observations that are
the most similar between classes, and hence represents the border between
classes. To draw conclusions on the features used for prediction, it is
perhaps most reasonable to adapt a conservative interpretation in which
predictive models is used to identify the most relevant features that are
later tested in follow-up experiments better suited to elucidating their
relationship to the variable of interest.

To conclude on predictive modeling with a practical note for connectome
comparison, we would like to stress that, while machine learning
algorithms are powerful tools, they work best if they are provided with
discriminant and noiseless features. In other words, as with all other
connectome comparison methods, optimizing first-level analysis
--subject-level connectome extraction-- is paramount.
